A statistical analysis of a counterstrike game: Boston 2018

### 2019-12-12 inst/counterstrike.Rmd
whitespace, more compact display

```{r, zachslist}
zachslist <- list(
    round1 =
      c("Skadoodle","olofmeister","tarik",
        "GuardiaN", "RUSH", "rain","Stewie2k",
        "karrigan","autimatic","NiKo"
        ),
    round2 =
      c("karrigan", "NiKo", "Stewie2K",
        "RUSH", "rain", "GuardiaN",
        "autimatic", "olofmeister"
        ),
    round3 =
      c("rain","tarik","autimatic",
        "karrigan","RUSH","GuardiaN",
        "Stewie2K","NiKo","olofmeister"
        ),
    round4 =
      c("rain","GuardiaN","karrigan",
        "NiKo","olofmeister"
        ),
    round5 =
      c("olofmeister","rain","karrigan",
        "tarik","Stewie2K","autimatic"
        ),
    round6 =
      c("GuardiaN","karrigan")
)
```

>>>>

```{r, zachslist}
zachslist <- list(
    round1 = c("Skadoodle","olofmeister","tarik","GuardiaN","RUSH",
         "rain", "Stewie2k","karrigan","autimatic","NiKo"),
    round2 = c("karrigan", "NiKo", "Stewie2K", "RUSH", "rain", "GuardiaN",
         "autimatic", "olofmeister"),
    round3 = c("rain","tarik","autimatic", "karrigan","RUSH","GuardiaN",
         "Stewie2K","NiKo","olofmeister"),
    round4 = c("rain","GuardiaN","karrigan", "NiKo","olofmeister"),
    round5 = c("olofmeister","rain","karrigan", "tarik","Stewie2K","autimatic"),
    round6 = c("GuardiaN","karrigan")
)
```
